---
title: "Oz"
subtitle: "Project Gutenberg Text Mining"
output: html_document
---

```{r setup, include = F}
knitr::opts_chunk$set(fig.width = 10, fig.height = 8, fig.retina = 2)
library(tidyverse)
library(rmarkdown)
source("R/Single_Word_Analysis.R")
```

# Text Mining of Oz Series

I originally downloaded the Oz series of books from Project Gutenberg. However, I didn't want to keep downloading it everything I made a minor change to this file. So I'm including my download code below, but loading the data from a saved file.

```{r download_oz, eval = FALSE}
oz <- single_word_unnested(gather_gutenberg_books(
  c(55, 55, 420, 419, 517, 486, 485, 955, 957, 956, 25581, 24459, 30852, 961),
  c("The Wonderful Wizard of Oz", "The Marvelous Land of Oz", "Dorothy and the Wizard", "The Magic of Oz", "The Emerald City of Oz", "Ozma of Oz", "The Road to Oz", "The Patchwork Girl of Oz", "The Scarecrow of Oz", "Tik-Tok of Oz", "Rinkitink in Oz", "The Lost Princess of Oz", "The Tin Woodman of Oz", "Glinda of Oz")))
```

Here is the code loading the Oz data saved in the Data folder.
```{r load_oz_from_file, cache = T}
oz <- readRDS("Data/Oz.RData")
oz <- single_word_unnested(oz)
```

This collection of charts shows the most common words in the Oz Series. It is broken up into two sets of charts. The first chart shows the tops words in all the books, followed by the top words in each individual book. There is also a wordcloud, but I've turned that off for now.
```{r show_top_words_one_chart, fig.height = 6}
single_word_review_one_chart(oz, show_top_words = 25)
```

```{r show_top_10_words}
single_word_review(oz, show_top_words = 10, number_of_columns = 3)
```

```{r cloud, eval = FALSE}
single_word_cloud(oz)
```


```{r sentimental_analysis_cleaning}
remove_oz_words = c("cowardly", "wicked", "witch", "magic", "buggy")

single_word_sentiment_cleaning(oz, remove_words = remove_oz_words, words_shown = 5, number_of_columns = 3)
```

```{r sentimental_analysis, fig.height = 10}
single_word_sentiment(oz, number_of_columns = 3, remove_words = remove_oz_words)
```


